Modelling the emergence of whisker barrels

### 2020-07-11 paper/briefpaper/brief.tex
One more suggestion from Leah, not addressed in previous commmit

\MPthreePred{To further investigate the interplay of genetic and intrinsic
  mechanisms we simulated two well known experimental manipulations of barrel
  development. First, we simulated a seminal barrel duplication paradigm}
\citep{shimogori_fibroblast_2005,assimacopoulos_fibroblast_2012}
\MPthreePred{in which the growth factor Fgf8, which is normally expressed at
  the anterior end of the cortical subplate from around E9.5}
\citep{crossley_mouse_1995}, \MPthreePred{is ectopically expressed (by
  electroporation) also at the posterior pole. We assume that this results in
  a mirror of the primary barrel cortex boundary along the rostrocaudal axis}
\citep{assimacopoulos_fibroblast_2012} \MPthreePred{and a mirroring of the
  anterior-posterior guidance gradient $\rho_1$ at the border between them
  (Fig.\,\ref{fig:fgf8}A). The result after 30000 iterations, and otherwise
  using the parameters of the example simulation, was two mirror-symmetrical
  barrel fields comprising $2N$ barrels (Fig.\,\ref{fig:fgf8}B), consistent
  with the outcome of the original experiments.}

>>>>

\MPthreePred{To further investigate the interplay of genes intrinsic to the
  developing neocortex and extrinsic factors such as thalamocortical input,
  we simulated two well known experimental manipulations of barrel
  development. First, we simulated a seminal barrel duplication paradigm}
\citep{shimogori_fibroblast_2005,assimacopoulos_fibroblast_2012}
\MPthreePred{in which the growth factor Fgf8, which is normally expressed at
  the anterior end of the cortical subplate from around E9.5}
\citep{crossley_mouse_1995}, \MPthreePred{is ectopically expressed (by
  electroporation) also at the posterior pole. We assume that this results in
  a mirror of the primary barrel cortex boundary along the rostrocaudal axis}
\citep{assimacopoulos_fibroblast_2012} \MPthreePred{and a mirroring of the
  anterior-posterior guidance gradient $\rho_1$ at the border between them
  (Fig.\,\ref{fig:fgf8}A). The result after 30000 iterations, and otherwise
  using the parameters of the example simulation, was two mirror-symmetrical
  barrel fields comprising $2N$ barrels (Fig.\,\ref{fig:fgf8}B), consistent
  with the outcome of the original experiments.}
